---
title: "exploreR"
author: "Milos Milic, Jim Pushor, Arzan Irani, Rachel Riggs"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{exploreR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Welcome to exploreR! This is a small package that will provide very useful summaries of your data frame. It is best used before your exploratory data analysis. The package is composed of three functions. The instructions below will explain the use and the specific output based on the data frame input provided for the function.

You can use the data frame to see how the functions work.

```{r}
toy_data <- data.frame("letters" = c("a", "b", "c", "d"),
                       "numbers" = c(1, 4, 6, 5),
                       "booleans" = c(TRUE, FALSE, FALSE, TRUE),
                       stringsAsFactors = FALSE)

```

#### Function 1 | Variable summary

This function will take in one argument(a data frame) and return a data frame.
```{r}
#variable_summary(toy_data)

```

Using our `toy_data` example, `variable_summary()` would return the following data frame.

| variable_type | count |
| ------------- | ----- |
| numeric       | 1     |
| character     | 1     |
| boolean       | 1     |
| date          | 0     |
| other         | 0     |



#### Function 2 | Missing values per variable

For this function we will use a modified data frame. This function takes in the single data frame argument and returns the amount of empty cells and a percentage of empty cells compared to the length of the column.

```{r}
toy_data_2 <- data.frame("letters" = c("a", "b", NA, "d"),
                       "numbers" = c(1, 4, 6, NA),
                       "booleans" = c(NA, FALSE, NA, TRUE),
                       stringsAsFactors = FALSE)

#missing_values(toy_data_2)

```

Using our `toy_data_2` example, `missing_values()` would return the following data frame.

| variable      | missing_values | percent_missing |
| ------------- | ----- | ------ |
| letters | 1     | 0.25      |
| numbers | 1   | 0.25   |
| booleans | 2     | 0.5      |



#### Function3 | Dataset Size/Info

This function will take in one argument(a data frame) and will provide a short summary of the data frame.



```{r}

#size(toy_data)

```

Using our `toy_data` example, `size()` would return the following data frame.


example output of `size`:

| rows  | columns | size_in_memory |
| ----- | ------- | -------------- |
| 4  | 3     | 0.02mb         |




